---
title: "Seoul Bike Dataset"
author: "Andrew Danda, 구민우, 방설화"
date: "`r Sys.Date()`"
documentclass: article
fontsize: 11pt 
geometry: margin=0.7in
output: pdf_document
header-includes:
  - \usepackage{kotex}
  - \usepackage{palatino}
  - \usepackage{enumerate}
  - \usepackage[onehalfspacing]{setspace}
  - \usepackage{hyperref}
  - \usepackage{amsthm}
  - \usepackage{enumitem}
  - \newtheoremstyle{sol}{3pt}{2pt}{}{}{\bfseries}{.}{.5em}{}
  - \theoremstyle{sol}
  - \newtheorem*{sol}{Suggested Solution}
  - \newcommand{\benum}{\begin{enumerate}}
  - \newcommand{\eenum}{\end{enumerate}}
  - \newcommand{\bitem}{\begin{itemize}}
  - \newcommand{\eitem}{\end{itemize}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, prompt=FALSE, message = FALSE,comment=NA )
```

This is a dataset containing Seoul Bike sharing ridership from December 1, 2017 to November 30, 2018.  The objective is to predict the number of riders on at any given time across the year given the data shown in this dataset

\small
\begin{center}
\centering
\begin{table}[htb!]
\centering
\begin{tabular}{cl}
\hline 
\multicolumn{2}{c}{Dependent variable}\\
\hline 
$Rented_Bike_Count$&The number of bikes rented\\
\hline \hline	
\multicolumn{2}{c}{Independent variables} \\
\hline
\multicolumn{2}{l}{1. Time Varibles} \\
\hline
$Date$&The Date (dd/mm/yyyy)\\
$Hour$&The Hour (integer between 1 and 24))\\
$Holiday$&Dummy variable if that day is a holiday or not\\
$FunctionalDay$&Dummy variable if the bikes were functional or not\\
$Seasons_Spring$&Dummy variable if the season is Spring or not\\
$Seasons_Summer$&Dummy variable if the season is Summer or not\\
$Seasons_Autumn$&Dummy variable if the season is Autumn or not\\
$Seasons_Winter$&Dummy variable if the season is Winter or not\\
\hline 
\multicolumn{2}{l}{2. Weather varibles}\\
\hline
$Temperature$&Temperature in Celsius\\
$Humidity$&Humidity ($\%$)\\
$Wind_Speed$&Wind speed in meters per second\\
$Visibility$&Visibility in Kilometers\\
$Dew_Point_Temperature$&Dew Point Temperature in Celsius\\
$Solor_Radiation$&Solar Radiation in MJ/m2\\
$Rainfall$&Rainfall in millimeters\\
$Snowfall$&Snowfall in centimeters\\
\hline
\end{tabular}
\end{table}
\end{center}
\normalsize

## The Dataset
```{r librarys}
library(tidyverse)
library(dplyr)
library(fastDummies)
```

```{r data}
bikeData <- read.csv("SeoulBikeData.csv", stringsAsFactors=FALSE, fileEncoding="latin1")

# Clean dataset

# rename columns
bikeData <- bikeData %>%
  rename("Rented_Bike_Count" = "Rented.Bike.Count",
         "Temperature" = "Temperature..C.",
         "Humidity" = "Humidity...",
         "Wind_Speed"= "Wind.speed..m.s.",
         "Visibility" = "Visibility..10m.",
         "Dew_Point_Temperature" = "Dew.point.temperature..C.",
         "Solar_Radiation" = "Solar.Radiation..MJ.m2.",
         "Rainfall" = "Rainfall.mm.",
         "Snowfall" = "Snowfall..cm.",
         "Functioning_Day" = "Functioning.Day")

#divide the visibility by 100 to change it's units from 10s of meters to kilometers
bikeData$Visibility <- bikeData$Visibility / 100

# Dummy varibles
bikeData$Holiday <- ifelse(bikeData$Holiday == "No Holiday", 0, 1)
bikeData$Functioning_Day <- ifelse(bikeData$Functioning_Day == "Yes", 1, 0)

#Holiday Dummies
bikeData <- bikeData %>% dummy_cols(select_columns = c("Seasons"))

summary(bikeData)
```

