---
title: "Seoul Bike Dataset"
author: "Andrew Danda, 구민우, 방설화"
date: "`r Sys.Date()`"
documentclass: article
fontsize: 11pt 
geometry: margin=0.7in
output: pdf_document
header-includes:
  - \usepackage{kotex}
  - \usepackage{palatino}
  - \usepackage{enumerate}
  - \usepackage[onehalfspacing]{setspace}
  - \usepackage{hyperref}
  - \usepackage{amsthm}
  - \usepackage{enumitem}
  - \newtheoremstyle{sol}{3pt}{2pt}{}{}{\bfseries}{.}{.5em}{}
  - \theoremstyle{sol}
  - \newtheorem*{sol}{Suggested Solution}
  - \newcommand{\benum}{\begin{enumerate}}
  - \newcommand{\eenum}{\end{enumerate}}
  - \newcommand{\bitem}{\begin{itemize}}
  - \newcommand{\eitem}{\end{itemize}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, prompt=FALSE, message = FALSE,comment=NA )
```

This is a dataset containing Seoul Bike sharing ridership from December 1, 2017 to November 30, 2018.  The objective is to predict the number of riders on at any given time across the year given the data shown in this dataset

\small
\begin{center}
\centering
\begin{table}[htb!]
\centering
\begin{tabular}{cl}
\hline 
\multicolumn{2}{c}{Dependent variable}\\
\hline 
$Rented_Bike_Count$&The number of bikes rented\\
\hline \hline	
\multicolumn{2}{c}{Independent variables} \\
\hline
\multicolumn{2}{l}{1. Time Varibles} \\
\hline
$Date$&The Date\\
$Hour$&The Hour (between 1 and 24)\\
$Holiday$&Dummy varible if that day is a holiday or not\\
$FunctionalDay$&Not sure what this is lol\\
\hline 
\multicolumn{2}{l}{2. Weather varibles}\\
\hline
$Temperature$&Temperature in Celsius\\
$Humidity$&Humidity ($\%$)\\
$Wind_Speed$&Windspeed in meters per second\\
$Visibility$&Visibility (10m)\\
$Dew_Point_Temperature$&Dew Point Temperature in Celsius\\
$Solor_Radiation$&Solor Radiation in MJ/m2\\
$Rainfall$&Rainfall in millimeters\\
$Snowfall$&Snowfall in centimeters\\
\hline
\end{tabular}
\end{table}
\end{center}
\normalsize

## The Dataset
```{r librarys}
library(tidyverse)
library(dplyr)
library(fastDummies)
```

```{r data}
bikeData <- read.csv("SeoulBikeData.csv", stringsAsFactors=FALSE, fileEncoding="latin1")

# Clean dataset

# rename columns
bikeData <- bikeData %>%
  rename("Rented_Bike_Count" = "Rented.Bike.Count",
         "Temperature" = "Temperature..C.",
         "Humidity" = "Humidity...",
         "Wind_Speed"= "Wind.speed..m.s.",
         "Visibility" = "Visibility..10m.",
         "Dew_Point_Temperature" = "Dew.point.temperature..C.",
         "Solar_Radiation" = "Solar.Radiation..MJ.m2.",
         "Rainfall" = "Rainfall.mm.",
         "Snowfall" = "Snowfall..cm.",
         "Functioning_Day" = "Functioning.Day")

# Dummy varibles
bikeData$Holiday <- ifelse(bikeData$Holiday == "No Holiday", 0, 1)
bikeData$Functioning_Day <- ifelse(bikeData$Functioning_Day == "Yes", 1, 0)

#Holiday Dummies
bikeData <- bikeData %>% dummy_cols(select_columns = c("Seasons"))

summary(bikeData)
```

