---
title: "Seoul Bike Dataset"
author: "Andrew Danda, 구민우, 방설화"
date: "`r Sys.Date()`"
documentclass: article
fontsize: 11pt 
geometry: margin=0.7in
output: pdf_document
header-includes:
  - \usepackage{kotex}
  - \usepackage{palatino}
  - \usepackage{enumerate}
  - \usepackage[onehalfspacing]{setspace}
  - \usepackage{hyperref}
  - \usepackage{amsthm}
  - \usepackage{enumitem}
  - \newtheoremstyle{sol}{3pt}{2pt}{}{}{\bfseries}{.}{.5em}{}
  - \theoremstyle{sol}
  - \newtheorem*{sol}{Suggested Solution}
  - \newcommand{\benum}{\begin{enumerate}}
  - \newcommand{\eenum}{\end{enumerate}}
  - \newcommand{\bitem}{\begin{itemize}}
  - \newcommand{\eitem}{\end{itemize}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, prompt=FALSE, message = FALSE,comment=NA )
```
# Question
Can we predict the number of riders using the Seoul Bike Sharing based on the date and the weather?

# Methods
We plan on using Lasso, Ridge, Decision tree and Random forest for this Dataset.

## The Dataset

This is a dataset containing Seoul Bike sharing ridership from December 1, 2017 to November 30, 2018.

\small
\begin{center}
\centering
\begin{table}[htb!]
\centering
\begin{tabular}{cl}
\hline 
\multicolumn{2}{c}{Dependent variable}\\
\hline 
$Rented_Bike_Count$&The number of bikes rented\\
\hline \hline	
\multicolumn{2}{c}{Independent variables} \\
\hline
\multicolumn{2}{l}{1. Time Varibles} \\
\hline
$Date$&The Date (dd/mm/yyyy)\\
$Hour$&The Hour (integer between 1 and 24)\\
$Holiday$&Dummy variable if the day is a holiday or not\\
$Weekend$&Dummy variable if the day is a weekend or not\\
$wkdhol$&Dummy variable.  Merged Holiday and Weekend variables together\\
$FunctionalDay$&Dummy variable if the bikes were functional or not\\
$Seasons_Spring$&Dummy variable if the season is Spring or not\\
$Seasons_Summer$&Dummy variable if the season is Summer or not\\
$Seasons_Autumn$&Dummy variable if the season is Autumn or not\\
$Seasons_Winter$&Dummy variable if the season is Winter or not\\
\hline 
\multicolumn{2}{l}{2. Weather varibles}\\
\hline
$Temperature$&Temperature in Celsius\\
$Humidity$&Humidity ($\%$)\\
$Wind_Speed$&Wind speed in meters per second\\
$Visibility$&Visibility in Kilometers\\
$Dew_Point_Temperature$&Dew Point Temperature in Celsius\\
$Solor_Radiation$&Solar Radiation in millijoules Per square meter\\
$Rainfall$&Rainfall in millimeters\\
$Snowfall$&Snowfall in centimeters\\
\hline
\end{tabular}
\end{table}
\end{center}
\normalsize


```{r librarys}
library(tidyverse)
library(dplyr)
library(fastDummies)
```

```{r data}
bikeData <- read.csv("SeoulBikeData.csv", stringsAsFactors=FALSE, fileEncoding="latin1")

# Clean dataset

# rename columns
bikeData <- bikeData %>%
  rename("Rented_Bike_Count" = "Rented.Bike.Count",
         "Temperature" = "Temperature..C.",
         "Humidity" = "Humidity...",
         "Wind_Speed"= "Wind.speed..m.s.",
         "Visibility" = "Visibility..10m.",
         "Dew_Point_Temperature" = "Dew.point.temperature..C.",
         "Solar_Radiation" = "Solar.Radiation..MJ.m2.",
         "Rainfall" = "Rainfall.mm.",
         "Snowfall" = "Snowfall..cm.",
         "Functioning_Day" = "Functioning.Day")

#divide the visibility by 100 to change it's units from 10s of meters to kilometers
bikeData$Visibility <- bikeData$Visibility / 100

#add weekend variable
bikeData$Weekend <- ifelse(lubridate::wday(as.Date(bikeData$Date,format = "%d/%m/%Y"), week_start = 1) > 5,1,0)
#lubridate::wday(as.Date("21/04/2024",format = "%d/%m/%Y"),label = TRUE, week_start = 1)

# Dummy variables
bikeData$Holiday <- ifelse(bikeData$Holiday == "No Holiday", 0, 1)
bikeData$Functioning_Day <- ifelse(bikeData$Functioning_Day == "Yes", 1, 0)

#Holiday Dummies
bikeData <- bikeData %>% dummy_cols(select_columns = c("Seasons"))


#remove all data where functioning day is false
#We will only use data where the bikes are functioning.
bikeData <- bikeData %>% filter(Functioning_Day == 1)

#combine weekend with holidays
# let's use this variable instead of weekend and holidays.  
bikeData$wkdHol <- ifelse(bikeData$Holiday == 1 | bikeData$Weekend == 1, 1, 0)

# summary(bikeData)
```

``` {r trainDataset}

# Split dataset into test and train.
set.seed(42069)
train_index<-sample(c(TRUE,FALSE),nrow(bikeData),replace=TRUE, prob=c(.8,.2))

bikeData.train <- bikeData[train_index,]
bikeData.test <- bikeData[!train_index,]

#Check number of observations
nrow(bikeData.train)
nrow(bikeData.test)

```

